Binding of cations to phospholipid bilayers

### 2015-02-12 LIPIDionINTERACT/LIPIDionINTERACT.tex
update ion-lipid interactions manuscript

\author{Andrea Catte}
\thanks{University of East Anglia, Norwich, United Kingdom}
\author{Matti Javanainen}
\thanks{Tampere University of Technology, Tampere, Finland}
\author{Markus S. Miettinen}
\thanks{Fachbereich Physik, Freie Universit\"at Berlin, Berlin, Germany}
%\setcounter{page}{1}
\author{O. H. Samuli Ollila} 
\thanks{{\bf Author to whom correspondence may be addressed. E-mail: samuli.ollila@aalto.fi.}}
\thanks{Helsinki Biophysics and Biomembrane Group, Department of Biomedical Engineering and Computational Science, Aalto University, Espoo, Finland}
%\footnote{Author to whom 
%correspondence may be addressed. E-mail: samuli.ollila@aalto.fi.\\
%}
%\affiliation{
%  Helsinki Biophysics and Biomembrane Group,
%Department of Biomedical Engineering and Computational Science, Aalto University, Espoo, Finland
%}

@@

MacRog\cite{maciejewski14}\todoi{Is this the same as in the first manuscript for full hydration?}  & POPC & 0 & ? & ? & 0 & 0 & 0 & ? & ?&?  &?  \\
MacRog\cite{maciejewski14}\todoi{Matti Javanainen, please check the numbers and let us know if you share some files through Zenodo} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}  & POPC & ? (NaCl) & ? & ? & ? & ? & ? & ? & ?&?  &?  \\
MacRog\cite{maciejewski14}\todoi{Matti Javanainen, please check the numbers and let us know if you share some files through Zenodo} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}        & POPC &  ? (NaCl) & ? & ? & ? & ? & ? & ? & ?&?  &?  \\
MacRog\cite{maciejewski14}\todoi{Matti Javanainen, please check the numbers and let us know if you share some files through Zenodo} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}        & POPC &   ? (NaCl) & ? & ? & ? & ? & ? & ? & ?&?  &?  \\
MacRog\cite{maciejewski14}\todoi{Matti Javanainen, please check the numbers and let us know if you share some files through Zenodo} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}        & POPC &   ? (NaCl) & ? & ? & ? & ? & ? & ? & ?&?  &?  \\

@@

\subsubsection{MacRog}
\todo{Matti Javanainen, please deliver the details.}

>>>>

\author{Andrea Catte}
\thanks{The authors are listed in alphaphetical order.}
\thanks{The author list is not completed.}
\thanks{University of East Anglia, Norwich, United Kingdom}
\author{Matti Javanainen}
\thanks{Tampere University of Technology, Tampere, Finland}
\author{Markus S. Miettinen}
\thanks{Fachbereich Physik, Freie Universit\"at Berlin, Berlin, Germany}
%\setcounter{page}{1}
\author{Vasily S. Oganesyan}
\thanks{University of East Anglia, Norwich, United Kingdom}
\author{O. H. Samuli Ollila} 
\thanks{{\bf Author to whom correspondence may be addressed. E-mail: samuli.ollila@aalto.fi.}}
\thanks{Helsinki Biophysics and Biomembrane Group, Department of Biomedical Engineering and Computational Science, Aalto University, Espoo, Finland}
%\footnote{Author to whom 
%correspondence may be addressed. E-mail: samuli.ollila@aalto.fi.\\
%}
%\affiliation{
%  Helsinki Biophysics and Biomembrane Group,
%Department of Biomedical Engineering and Computational Science, Aalto University, Espoo, Finland
%}

@@

MacRog\cite{maciejewski14}\todoi{DONE}  & POPC & 0 & 288 & 14400 & 0 & 0 & 0 & 310 & 90&40  &~\cite{macrogdehydFILES}  \\
MacRog\cite{maciejewski14}\todoi{DONE} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}  & POPC & 100 (NaCl) & 288 & 14554 & 27 & 0 & 27 & 310 & 90&50  & \cite{macrogIONfiles} \\
MacRog\cite{maciejewski14}\todoi{DONE} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}        & POPC &  200 (NaCl) & 288 & 14500 & 54 & 0 & 54 & 310 & 90&50  &\cite{macrogIONfiles}  \\
MacRog\cite{maciejewski14}\todoi{DONE} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}        & POPC &   300 (NaCl) & 288 & 14446 & 81 & 0 & 81 & 310 & 90&50  & \cite{macrogIONfiles} \\
MacRog\cite{maciejewski14}\todoi{DONE} , ionFF~\cite{??}\todoi{Appropriate reference for the ion model?}        & POPC &   400 (NaCl) & 288 & 14392 & 108 & 0 & 108 & 310 & 90& 50  & \cite{macrogIONfiles}  \\

@@

\subsubsection{MacRog}
\todo{DONE}
The simulation parameters are identical to those employed in our earlier study~\cite{botan15} for the full 
hydration and dehydration simulations. The initial structures with varying amounts of NaCl were constructed from an 
extensively hydrated bilayer by replacing water molecules with ions using the gromacs tool genion. Even at the highest 
considered salt concentration, the amount of water molecules per lipid after this replacement process was still greater than 50.
